UniScatter: Unifying Symbiotic Radio and Reconfigurable Intelligent Surface

### 2022-07-30 main.tex
:pencil: Update BTLS
:construction: Add instructions

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}

\begin{document}
\title{Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	}
}
\maketitle

\begin{abstract}
	% Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of ambient signals.
	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.

@@

	% Compared to conventional \gls{irs}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
	Compared to existing \gls{irs}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{irs} via smart input design.
	% Compared to \gls{irs}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.

@@

	% On the other hand, \gls{irs} has recently emerged as a promising technique to enhance the energy efficiency.
	% In practice, an \gls{irs} consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
	% Different from relay, backscatter and frequency-selective surface \cite{Anwar2018}, \gls{irs} assists the primary transmission using passive components with much lower energy consumption and thermal noise, but is limited to frequency-dependent reflection.
	% On the other hand, \gls{irs} consists of numerous sub-wavelength passive elements that alter propagation environment using adaptive backscatter pattern to assist existing networks. Extensive research has been devoted to optimizing the reflection coefficient
	% On the other hand, \gls{irs} consists of numerous sub-wavelength passive elements with adaptive amplitudes and/or phases that alter propagation environment to assist existing networks.
	On the other hand, \gls{irs} alters propagation environment for legacy networks using numerous sub-wavelength passive elements with adaptive amplitudes and/or phases.

@@

	% In contrast, dynamic passive beamforming that adjusts \gls{irs} within channel block was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
	% In contrast, dynamic passive beamforming that adjusts \gls{irs} over finer time slots was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
	Besides, \cite{Yang2020} proposed a dynamic passive beamforming that further adjusts \gls{irs} over fine-grained time slots for \gls{ofdm} systems to balance beamforming gain and multiuser diversity.

@@

	% For multiuser \gls{wpt}, \cite{Qiu2022} also reported that despite \gls{irs} is restricted to single-beam reflection, dynamic beamforming can mimic multi-beam reflection in a time-division manner and reduce the phase extraction loss.

@@

	% However, dynamic passive beamforming demands additional computational complexity and control overhead, and the performance-cost tradeoff needs reconsideration especially when the number of \gls{irs} elements is large.

@@

	Although dynamic passive beamforming artificially creates temporal diversity for flexible channel reconfiguration and resource allocation, it demands additional computational cost and control overhead, and the tradeoff deserves further attention especially for large \gls{irs}.
	In \cite{Chen2021,Zhang2021d}, \gls{irs} was also introduced to single- and multi-node \gls{sr} systems to reduce the total transmit power.
	When joint transmitter-\gls{irs} encoding is possible, \cite{Karasik2019} proved using \gls{irs} only for passive beamforming is generally suboptimal in terms of achievable rate for finite input constellations.
	% The capacity-achieving \gls{irs} strategy was found to
	Recently, \gls{irs}-empowered \gls{sr} was introduced in \cite{Xu2020b,Hua2022,Hu2021a} where independent passive beamforming and backscatter encoding were combined using advanced architectures.
	The authors of \cite{Xu2020b,Hua2022} proposed the \gls{irs} to modulate binary message over the whole phase shift matrix and the receiver to decodes from (non-coherent) primary to (coherent) backscatter link.
	In contrast, \cite{Hu2021a} divided the \gls{irs} into reflection and information elements, and evaluated the error performance of non-coherent backscatter detection.
	% Compared to existing \gls{irs}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{irs} via smart input design.

	To the best of our knowledge, all existing \gls{sr} literatures assumed backscatter modulation employs either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a} or finite equiprobable inputs \cite{Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022,Hu2021a}.
	The former is impractical for passive nodes with constrained number of states, while the latter does not fully exploit \gls{csi} to boost achievable backscatter rate.
	Besides, most relevant designs \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} were built over ideal \gls{ml} or \gls{sic} receiver.
	However, the advantage of \gls{sic} is questionable because 1) it requires non-coherent primary encoding at the transmitter and re-encoding, precoding, and subtraction at the receiver, 2) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 3) the backscatter symbol period is typically much longer due to physical constraints.
	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	Motivated by those, we propose the concept of Metascatter, which adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
	% ! An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
	The contributions of this paper is summarized as follows.

	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{irs}.
	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to balance backscatter encoding and passive beamforming.
	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{irs}.
	When only considering backscatter performance, the distribution involves the highest entropy and Metascatter is essentially an \gls{ambc} node.

@@

	\begin{subsection}{IRS: Channel Reconfiguration}
		% \gls{irs} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}. For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
		\gls{irs} elements assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
		For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ relates to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
		\end{equation}
		where $0 \le \beta_m \le 1$ is overall amplitude reflect ratio of state $m$.
		% Based on relevant \gls{csi}
	\end{subsection}
	% Tags periodically switch between different states to perform backscatter modulation.
	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	% \begin{equation}
	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
	% 	\label{eq:backscatter_modulation}
	% \end{equation}
	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

@@

				Input probability distribution and time block structure of \gls{sr}, \gls{irs}, and Metascatter.

@@

		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:metascatter}, Metascatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.} In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming. \gls{sr} and \gls{irs} can be regarded as extreme cases of Metascatter, where node input distribution boils down to uniform and deterministically biased, respectively.
		Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:metascatter}, Metascatter semi-randomly selects reflection state for each backscatter block, with \emph{guidance of input probability $P(\Gamma_m)$} for state $m$. In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming. \gls{sr} and \gls{irs} can be regarded as extreme cases of Metascatter, where node input distribution boils down to uniform and deterministic, respectively.

@@

		% \gls{sr} and \gls{irs} can be regarded as its extreme cases, where node input distribution boils down to uniform and deterministically biased, respectively.

@@

			Compared to conventional \gls{irs} literatures that optimize phase shifts under unit-module constraint, Metascatter starts from predefined reflection coefficients and designs their input distribution under sum-probability constraint to achieve flexible primary-backscatter tradeoff.

@@

					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})-\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}

@@

	\begin{subsection}{Input Distribution vs. Weight}
		\begin{figure}[!t]
			\centering
			\subfloat[Instance 1\label{fi:distribution_weights_1}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_1.tex}
				}
			}
			\subfloat[Instance 2\label{fi:distribution_weights_2}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_2.tex}
				}
			}
			\caption{Typical input distributions vs. weight $\rho$ for a Metascatter with $M=4$ inputs.}
			\label{fi:distribution_weights}
		\end{figure}
		% We consider a single Metascatter with $M=4$ inputs in this case of study.
		In Fig. \ref{fi:distribution_weights}, we present typical input distributions of a single Metascatter with $M=4$ inputs under different weight $\rho$.
		Fig. \subref*{fi:distribution_weights_1} and \subref*{fi:distribution_weights_2} are obtained from \gls{iid} drop and channel realizations.
		We note that even for $\rho=0$ (i.e., best backscatter performance), the optimal input distribution is not equiprobable like \gls{sr}, and adaptive channel coding can further increase total backscatter rate based on \gls{csi}.
		On the other hand, the optimal input distribution becomes fully deterministic at $\rho=1$ (i.e., best primary performance), where the state maximizes equivalent primary channel \eqref{eq:equivalent_channel} strength is chosen with probability \num{1}.
		In this case, Metascatter boils down to an \gls{irs} element with $M$ discrete states.
		As $\rho$ moves from \num{0} to \num{1}, the optimal input distribution becomes gradually biased to one state and flexibly balances the primary-backscatter tradeoff.
	\end{subsection}

@@

		Fig. \subref*{fi:region_coverage} shows the tradeoff between coverage disk radius $r$ and achievable rate region.
		When nodes are far from the user, both primary and backscatter rates decrease due to the product pass loss of forward and backward channels.
		Under the assumption of ideal backscatter decoding and re-encoding, Fig. \subref*{fi:region_duration} suggests using lower symbol period ratio $N$ can boost total backscatter rate per primary symbol.
		However, it requires more frequent detection and re-encoding at the user to maintain the primary rate.
		When $N$ becomes sufficiently large, total backscatter rate approaches \num{0} and Metascatters boil down to conventional \gls{irs} elements with fixed reflection patterns during whole channel block.
		In Fig. \subref*{fi:region_frequency}, we observe that passive Metascatter achieves higher backscatter rate at lower carrier frequency because of preferable propagation loss.
		Finally, \subref*{fi:region_noise} prove the performance of energy detection is robust for a wide range of noise power.
	\end{subsection}
\end{section}

\begin{section}{Conclusion}
	This paper introduced Metascatter that adapts input distribution of passive backscatter nodes to simultaneously transmit and assist over existing wireless systems.
	Starting from backscatter principles, we showed how Metascatters bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{irs} via smart input design.
	An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	To characterize achievable primary-backscatter rate region, we proposed a \gls{bcd} algorithm that evaluates \gls{kkt} input distribution in closed form, optimizes active beamforming by \gls{pgd}, and refines decision regions by existing methods.
	Numerical results demonstrated the advantage of adaptive node input distribution design for both primary and backscatter subsystems.

>>>>

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}

\begin{document}
% \title{UniScatter: Unifying Backscatter Communication, Reconfigurable Intelligent Surface, and Symbiotic Radio}
\title{UniScatter: Unifying Symbiotic Radio and Reconfigurable Intelligent Surface}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	}
}
\maketitle

\begin{abstract}
	% Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of ambient signals.
	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	% Scattering/reflection elements to
	% An RIS is a thin surface composed of N elements, each being a reconfigurable scatterer: a small antenna that receives and re-radiates without amplification, but with a configurable time delay [3]. For narrowband signals, this delay corresponds to a phase shift.

	Scatterers can harvest energy from, modulate information over, and reconfigure propagation of ambient radio waves.
	In backscatter communication,
	% ! Φ(c[n]) vs P

	% TODO
	back comms, symbiotic radio and RIS have appeared as three different and somewhat unrelated wireless technologies, explaining the key feature of each of them. Then I would say we introduce metascatter as a new paradigm that unifies and generalizes those three ...., explain the key feature of metascatter.

@@

	% Compared to conventional \gls{ris}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{ris} as extreme cases.
	Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
	% Compared to \gls{ris}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{ris} as extreme cases.

@@

	% On the other hand, \gls{ris} has recently emerged as a promising technique to enhance the energy efficiency.
	% In practice, an \gls{ris} consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
	% Different from relay, backscatter and frequency-selective surface \cite{Anwar2018}, \gls{ris} assists the primary transmission using passive components with much lower energy consumption and thermal noise, but is limited to frequency-dependent reflection.
	% On the other hand, \gls{ris} consists of numerous sub-wavelength passive elements that alter propagation environment using adaptive backscatter pattern to assist existing networks. Extensive research has been devoted to optimizing the reflection coefficient
	% On the other hand, \gls{ris} consists of numerous sub-wavelength passive elements with adaptive amplitudes and/or phases that alter propagation environment to assist existing networks.
	On the other hand, \gls{ris} alters propagation environment for legacy networks using numerous sub-wavelength passive elements with adaptive amplitudes and/or phases.

@@

	% In contrast, dynamic passive beamforming that adjusts \gls{ris} within channel block was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
	% In contrast, dynamic passive beamforming that adjusts \gls{ris} over finer time slots was proposed in \cite{Yang2020} to create diversity for \gls{ofdm} systems.
	Besides, \cite{Yang2020} proposed a dynamic passive beamforming that further adjusts \gls{ris} over fine-grained time slots for \gls{ofdm} systems to balance beamforming gain and multiuser diversity.

@@

	% For multiuser \gls{wpt}, \cite{Qiu2022} also reported that despite \gls{ris} is restricted to single-beam reflection, dynamic beamforming can mimic multi-beam reflection in a time-division manner and reduce the phase extraction loss.

@@

	% However, dynamic passive beamforming demands additional computational complexity and control overhead, and the performance-cost tradeoff needs reconsideration especially when the number of \gls{ris} elements is large.

@@

	Although dynamic passive beamforming artificially creates temporal diversity for flexible channel reconfiguration and resource allocation, it demands additional computational cost and control overhead, and the tradeoff deserves further attention especially for large \gls{ris}.
	In \cite{Chen2021,Zhang2021d}, \gls{ris} was also introduced to single- and multi-node \gls{sr} systems to reduce the total transmit power.
	When joint transmitter-\gls{ris} encoding is possible, \cite{Karasik2019} proved using \gls{ris} only for passive beamforming is generally suboptimal in terms of achievable rate for finite input constellations.
	% The capacity-achieving \gls{ris} strategy was found to
	Recently, \gls{ris}-empowered \gls{sr} was introduced in \cite{Xu2020b,Hua2022,Hu2021a} where independent passive beamforming and backscatter encoding were combined using advanced architectures.
	The authors of \cite{Xu2020b,Hua2022} proposed the \gls{ris} to modulate binary message over the whole phase shift matrix and the receiver to decodes from (non-coherent) primary to (coherent) backscatter link.
	In contrast, \cite{Hu2021a} divided the \gls{ris} into reflection and information elements, and evaluated the error performance of non-coherent backscatter detection.
	% Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.

	To the best of our knowledge, all existing \gls{sr} literatures assumed backscatter modulation employs either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a} or finite equiprobable inputs \cite{Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022,Hu2021a}.
	The former is impractical for passive nodes with constrained number of states, while the latter does not fully exploit \gls{csi} to boost achievable backscatter rate.
	Besides, most relevant designs \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} were built over ideal \gls{ml} or \gls{sic} receiver.
	However, the advantage of \gls{sic} is questionable because 1) it requires non-coherent primary encoding at the transmitter and re-encoding, precoding, and subtraction at the receiver, 2) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 3) the backscatter symbol period is typically much longer due to physical constraints.
	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{ris}.
	Motivated by those, we propose the concept of Metascatter, which adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{ris}.
	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{ris}.
	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
	% ! An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
	The contributions of this paper is summarized as follows.

	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{ris}.
	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to balance backscatter encoding and passive beamforming.
	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{ris}.
	When only considering backscatter performance, the distribution involves the highest entropy and Metascatter is essentially an \gls{ambc} node.

@@

	\begin{subsection}{IRS: Channel Reconfiguration}
		% \gls{ris} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}. For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
		\gls{ris} elements assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
		For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ relates to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
		\end{equation}
		where $0 \le \beta_m \le 1$ is overall amplitude reflect ratio of state $m$.
		% Based on relevant \gls{csi}
	\end{subsection}
	% Tags periodically switch between different states to perform backscatter modulation.
	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	% \begin{equation}
	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
	% 	\label{eq:backscatter_modulation}
	% \end{equation}
	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

@@

				Input probability distribution and time block structure of \gls{sr}, \gls{ris}, and Metascatter.

@@

		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:metascatter}, Metascatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.} In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming. \gls{sr} and \gls{ris} can be regarded as extreme cases of Metascatter, where node input distribution boils down to uniform and deterministically biased, respectively.
		Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:metascatter}, Metascatter semi-randomly selects reflection state for each backscatter block, with \emph{guidance of input probability $P(\Gamma_m)$} for state $m$. In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming. \gls{sr} and \gls{ris} can be regarded as extreme cases of Metascatter, where node input distribution boils down to uniform and deterministic, respectively.

@@

		% \gls{sr} and \gls{ris} can be regarded as its extreme cases, where node input distribution boils down to uniform and deterministically biased, respectively.

@@

			Compared to conventional \gls{ris} literatures that optimize phase shifts under unit-module constraint, Metascatter starts from predefined reflection coefficients and designs their input distribution under sum-probability constraint to achieve flexible primary-backscatter tradeoff.

@@

					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}

@@

	\begin{subsection}{Input Distribution vs. Weight}
		\begin{figure}[!t]
			\centering
			\subfloat[Instance 1\label{fi:distribution_weights_1}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_1.tex}
				}
			}
			\subfloat[Instance 2\label{fi:distribution_weights_2}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_2.tex}
				}
			}
			\caption{Typical input distributions vs. weight $\rho$ for a Metascatter with $M=4$ inputs.}
			\label{fi:distribution_weights}
		\end{figure}
		% We consider a single Metascatter with $M=4$ inputs in this case of study.
		In Fig. \ref{fi:distribution_weights}, we present typical input distributions of a single Metascatter with $M=4$ inputs under different weight $\rho$.
		Fig. \subref*{fi:distribution_weights_1} and \subref*{fi:distribution_weights_2} are obtained from \gls{iid} drop and channel realizations.
		We note that even for $\rho=0$ (i.e., best backscatter performance), the optimal input distribution is not equiprobable like \gls{sr}, and adaptive channel coding can further increase total backscatter rate based on \gls{csi}.
		On the other hand, the optimal input distribution becomes fully deterministic at $\rho=1$ (i.e., best primary performance), where the state maximizes equivalent primary channel \eqref{eq:equivalent_channel} strength is chosen with probability \num{1}.
		In this case, Metascatter boils down to an \gls{ris} element with $M$ discrete states.
		As $\rho$ moves from \num{0} to \num{1}, the optimal input distribution becomes gradually biased to one state and flexibly balances the primary-backscatter tradeoff.
	\end{subsection}

@@

		Fig. \subref*{fi:region_coverage} shows the tradeoff between coverage disk radius $r$ and achievable rate region.
		When nodes are far from the user, both primary and backscatter rates decrease due to the product pass loss of forward and backward channels.
		Under the assumption of ideal backscatter decoding and re-encoding, Fig. \subref*{fi:region_duration} suggests using lower symbol period ratio $N$ can boost total backscatter rate per primary symbol.
		However, it requires more frequent detection and re-encoding at the user to maintain the primary rate.
		When $N$ becomes sufficiently large, total backscatter rate approaches \num{0} and Metascatters boil down to conventional \gls{ris} elements with fixed reflection patterns during whole channel block.
		In Fig. \subref*{fi:region_frequency}, we observe that passive Metascatter achieves higher backscatter rate at lower carrier frequency because of preferable propagation loss.
		Finally, \subref*{fi:region_noise} prove the performance of energy detection is robust for a wide range of noise power.
	\end{subsection}
\end{section}

\begin{section}{Conclusion}
	This paper introduced Metascatter that adapts input distribution of passive backscatter nodes to simultaneously transmit and assist over existing wireless systems.
	Starting from backscatter principles, we showed how Metascatters bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
	An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	To characterize achievable primary-backscatter rate region, we proposed a \gls{bcd} algorithm that evaluates \gls{kkt} input distribution in closed form, optimizes active beamforming by \gls{pgd}, and refines decision regions by existing methods.
	Numerical results demonstrated the advantage of adaptive node input distribution design for both primary and backscatter subsystems.
